Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-07-11 draft/draft.tex
progress

@@

The following experiments are carried on.
\begin{enumerate}
\item 
Compute ratings and rankings from the full weighted networks.

@@

\item 
Compute ratings and rankings from sparsified versiond of the weighted networks, by removing a varying fraction of links sorted in decreasing order of absolute weight.
\end{enumerate}

>>>>

\section{
Data
\label{sec:data}
}

There are 5 leagues: England, France, Germany, Italy and Spain.
Each has 20 teams, with the exception of Germany.
In each league, each pair of teams plays two games, one as the local team and the other as the visitor.
In each game between the $i$-th and the $j$-th team, different metrics are measured.
With each metric, a weighted graphs of entries $w_{ij}\in \RR$ is obtained.

@@

The following experiments are carried on.
\begin{enumerate}
\item 
Compute ratings and rankings from the full weighted networks $w$ defining $f_{ij}=w_j-w_i$ for each pair $ij$ of a given league.

@@

\item 
Compute ratings and rankings from sparsified versiond of the weighted networks, by removing a varying fraction of links sorted in decreasing order of absolute weight.

\item 
Compute ratings defining the $f_{ij}=\phi_j-\phi_i$ where the strength $\phi_i = \sum_j w_{ij}$ defines a local potential for the $i$-th team.
\end{enumerate}
